Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-04-10 WRITEUP/ms.tex
address comments up to Sec 6

%mm rearranged and combined this and the following paragraph to proceed from observation to conclusion
Early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population. 
%
As a consequence, we expect them to be significantly more ionized, and have intense and hard interstelar radiation fields (ISRF). Since their metallicity and dust content are also expected to be lower in these early evolutionary stages, shielding of UV photons---responsible for the photoheating of the gas---  is strongly reduced. Such differences in turn affect the regulation of the thermal and chemical state of the multi-phase interstellar medium (ISM). Studying ISM properties of early galaxies is essential for understanding how \SF proceeds under more extreme conditions.
%
Even in the local Universe, where detailed \obs can be made, variations in 
%mm cloud
     MCC  \MM{do Hughes et al. study cloud complexes, as you do, or can you derive info about complexes from their data?}
     \DL{This is just a statement to say there are variations among local GMCs. Together with the different galaxy properties found for early galaxies, it is interesting to study properties of molecular structures at earlier epochs. }
properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).  Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of MCCs in early galaxies, and how do they differ from those found in local \galpop?}
%

@@

In cases where stellar component plays an important role in the dynamics, the virial parameter becomes
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G} \frac{M_{\rm cl} \sigma^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm cl} + M_{\star} }\,.
\label{eqn:alpha_tot}
\end{equation}

@@

% radiative feedback --> NT pressure
Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) 
%mm and OB/AGB stars. 
   as well as winds from OB and asymptotic giant branch stars.
Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell. The remaining energy is injected into the ISM in kinetic and thermal energy forms. Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).  
%mm
%   \MM{confirm:} 
Photoionization from local sources is neglected in this simulation
\citep[see][for its effect]{pallottini:2019,decataldo:2019}. 
%mm \AP{modified accordingly}

The simulation zooms in on a galaxy named
%mm 
   after the flower 
\flower whose properties are given in 
%mm \citet{Pallottini17b} 
      \citet{Pallottini17a} 
and are briefly summarized in the following. \flower is a Lyman-break galaxy 
%mm (LBG), [unused acronym]
that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm
  DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and
accretes mass from the IGM mainly via three filaments of length
$\simeq$\,100\,kpc. \flower has a stellar mass of
$M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of
$Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm
  H2}\simeq$\,5\E{7}\,\Msun, and a SFR of
%mm $\simeq$\,100\,\Msun\,yr\pmOne. [for consistency with the next subsection] 
   30--80 \Msun\,yr\pmOne. 
%mm \MM{What is its gas fraction?  I ask because its molecular gas
%mass is minuscule, particularly for such a high SFR: this is a
%depletion time of only 0.5 Myr, while modern galaxies usually have
%depletion times more like 0.5--2~Gyr!} \AP{the gas fraction is very
%flickering and depends on which radius we are considering, as the
%galaxy is actively accreating material and merging; depletion time
%are low, see the ssfr note added considering that $ssfr \propto
%t_{depletion}^{-1}$} 
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star}
\simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$
relation observed at high redshift \citep{Jiang2016}, which is higher
than normal local galaxies. The effective stellar radius of \flower
is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm
  200}\simeq$\,15\,kpc.

@@

Given \flower's SF stochastic nature, in this work we mostly focus on
the analysis of two of its most extreme evolutionary stages (see
\Sec{singless}). The two phases correspond to (a) intense accretion
(b) starburst (\Fig{SFH}). We are interesting in determining whether
MCC properties are sensitive to these different dynamical
conditions. For completeness, for the other evolutionary stages traced
in the simulation we only show scaling relations (see 
%mm [Figures must be numbered and placed in order cited.  Better to
%cite to the section and leave the figure in its proper place.] \Fig{alpha16-28}).
     Sect.~\ref{sec:ncut}).

@@

\subsection{Molecular Cloud Complex Properties}

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCCs is calculated from non-thermal
velocity dispersion $\sigma_{\rm NT}$ and thermal sound speed $c_s$ as
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas 
exceeds that from the diffuse gas. We therefore calculate each term on
the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.
%
The local sound speed of all identified molecular complexes is much
smaller than their turbulent velocities\footnote{Velocity dispersions
  calculated from velocity field are comparable to those calculated
  from the pressure field 
%mm
    \MM{The turbulent pressure field has not been
    mentioned in section 3, so you'll need to add a sentence there
    mentioning its presence and behavior to mention it here}, 
indicating that contribution from shear is unlikely to dominate the velocity dispersions reported here.\label{ftn:veldisp}}. 
On average, the Mach number of the MCCs identified at the highest density threshold is $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$, 
but this depends on the evolutionary stage of \flower.  % see e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to 
a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
However, not all evolutionary stages considered have at least one MCC at this highest density threshold, 
we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc) in the following. 
We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. 
%
The massive ($M_{\rm cl}>$10$^8$\,\Msun) 
clouds identified at low density cut (see top left panel of \Fig{dist})  
correspond to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. The mass of the MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. The stellar-to-gas mass ratio ranges ($M_{\star}/M_{\rm cl}$) between $<$\,0.1 to 70 over all the
MCCs identified across all evolutionary stages of \flower.

@@

@@

\subsection{Single Evolutionary Stage}  \label{sec:singless}
\AF{Description of the results is very chaotic. You mix evol. phases, properties, ncut, that is physical and numerical issues. Please reorder and make it more logical.}
We first focus on the two most extreme evolutionary stages of \flower---the accreting and starburst phases (see \Sec{sfh}), 
and identify a set of MCCs in each of them. \DL{note that delay in cloud properties and SFR.}
Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.

Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) 
and sizes ($R\simeq 100$\,pc). These values are consistent with those found in starburst galaxies, 
such as the nearby gas-rich galaxy M64 and 
% Kennicutt, 1996IAUS..171...11K
% Spiral gal, appears to have accreted a gas-rich companion in the recent past, 
% with the inner gas disk the remnant of the
% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995). 
the z\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
\citep{Rosolowsky05a, Swinbank11a}.
Since the sizes are somewhat dependent on the choice of $n_{\rm cut}$, as such, 
some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$. 
In this way, we identify a population of denser molecular structures (see \Fig{MCC}). 
On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.

%Now discuss sigma - R relation; poor statistcis. But how many MCCs do we have?

% Starburst 
In the starburst phase, some MCCs have lower velocity dispersion, virial parameter, 
and $\sigma^2/R$ compared to the accreting phase. \DL{Is this significant enough to say something physical? If so, not immediately clear to me what cause the differences.}
% PVE
We also compare the MCCs identified in our simulations to those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panels of \Fig{larsons_single}). Dashed lines in the figure show the loci along which the given external pressures are needed for MCCs to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).
The MCCs in the satellite galaxies are found to follow the locus of
$\log{(P/\textrm{K cm}^{-3})}$\eq6, \MM{This is not shown in the
  figure.  If you want to claim it, it needs to be shown somewhere.} which
is consistent with that found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a}.

% cloud structures at large and small scale
% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
% column density) as fundamental properties of molecular cloud structure.
Larson's third relation relates MCCs structures on small and large
scales via two physical properties: mass and size \citep{Larson81a,
  McKee07a}. This is also known as the constant column density
relation,
\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
  $\Sigma$.  Effectively, Larson's mass-size relation is a single
  point on that relationship, at the constant $\Sigma$ value.  This
  suggests that the mass-size relation is just an artifact of the
  narrow range of column densities observed with $^{12}CO$, as
  suggested among others by \citet{Ballesteros11}.}
 since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$). By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
\begin{equation}
A_v = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
\end{equation}
then, assuming spherical symmetry, the mass of an MCC can be expressed as a function of $A_v$ and its size $R$
\begin{equation}\label{eqn:constantcolumndensity}
M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
\end{equation}
where we have taken $\mu = 2.5$ as the mean molecular weight.

We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
%
In the same plot, we also show loci of constant surface densities,
which are parameterized through the visual extinction $A_V$. \MM{Why
  do you go through $A_v$ rather than just using surface densities
  directly?} As shown
in \Fig{MR}, the MCCs identified in \flower lie above this relation,
along the locus of $A_v \simeq 8.9$ clouds observed by
\citet{Lombardi10a} in the MW. \MM{Does the variation in surface
  density seen in Figure 6 correspond to the variation in $A_V$ seen
  here?}
%
%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

@@

\subsection{Temporal Evolution and Adopted Density Threshold Dependence}\label{sec:ncut}
% single Snapshot
We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs. That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
%
We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
%
In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
%
This lack of variation is reassuring, i.e. the dynamics of the MCCs are not artifacts or biased by our choice of $n_{\rm cut}$ on the scales studied in the present work. Our results are therefore robust to the various density cuts of choice.

@@

>>>>

%mm rearranged and combined this and the following paragraph to proceed from observation to conclusion
Early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population. 
%
As a consequence, we expect them to be significantly more ionized, and have intense and hard interstelar radiation fields (ISRF). Since their metallicity and dust content are also expected to be lower in these early evolutionary stages, shielding of UV photons---responsible for the photoheating of the gas---  is strongly reduced. Such differences in turn affect the regulation of the thermal and chemical state of the multi-phase interstellar medium (ISM). Studying ISM properties of early galaxies is essential for understanding how \SF proceeds under more extreme conditions.
%
Even in the local Universe, where detailed \obs can be made, variations in molecular cloud 
%       \MM{do Hughes et al. study cloud complexes, as you do, or can you derive info about complexes from their data?}
%     \DL{This is just a statement to say there are variations among local GMCs. Together with the different galaxy properties found for early galaxies, it is interesting to study properties of molecular structures at earlier epochs. }
properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).  Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of 
molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}
%

@@

In cases where stellar component plays an important role in the dynamics, the virial parameter becomes
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G} \frac{M_{\rm cl} \sigma^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm cl} + M_{\star} }\,,
\label{eqn:alpha_tot}
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.

@@

% radiative feedback --> NT pressure
Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) 
%mm and OB/AGB stars. 
   as well as winds from OB and asymptotic giant branch stars.
Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell. The remaining energy is injected into the ISM in kinetic and thermal energy forms. Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).  
\DL{AP: please elaborate non-thermal pressure here..}
Photoionization from local sources is neglected in this simulation
\citep[see][for its effect]{pallottini:2019,decataldo:2019}. 
%mm \AP{modified accordingly}

The simulation zooms in on a galaxy named
%mm 
   after the flower 
\flower whose properties are given in 
%mm \citet{Pallottini17b} 
      \citet{Pallottini17a} 
and are briefly summarized in the following. \flower is a Lyman-break galaxy 
%mm (LBG), [unused acronym]
that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm
  DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and
accretes mass from the IGM mainly via three filaments of length
$\simeq$\,100\,kpc. \flower has a stellar mass of
$M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of
$Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm
  H2}\simeq$\,5\E{7}\,\Msun, and a SFR of
%mm $\simeq$\,100\,\Msun\,yr\pmOne. [for consistency with the next subsection] 
   30\,--\,80\,\Msun\,yr\pmOne. 
%mm \MM{What is its gas fraction?  I ask because its molecular gas
%mass is minuscule, particularly for such a high SFR: this is a
%depletion time of only 0.5 Myr, while modern galaxies usually have
%depletion times more like 0.5--2~Gyr!} \AP{the gas fraction is very
%flickering and depends on which radius we are considering, as the
%galaxy is actively accreating material and merging; depletion time
%are low, see the ssfr note added considering that $ssfr \propto
%t_{depletion}^{-1}$} 
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star}
\simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$
relation observed at high redshift \citep{Jiang2016}, which is higher
than normal local galaxies. The effective stellar radius of \flower
is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm
  200}\simeq$\,15\,kpc.

@@

Given the stochastic nature of \flower in its star formation history, we mostly focus on
two of its most extreme evolutionary stages in this work (see \Sec{singless}).
The two phases correspond to (a) an intensely accreting phase and
(b) a starburst phase (\Fig{SFH}). We are interested in determining whether 
MCC properties are sensitive to these different dynamical
conditions. For completeness, we also show the scaling relations examined for the other evolutionary stages traced
in the simulation (see \Sec{ncut}).

@@

\subsection{Molecular Cloud Complex Properties} \label{sec:distribution}

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCCs is calculated from non-thermal
velocity dispersion $\sigma_{\rm NT}$ and thermal sound speed $c_s$ as
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas 
exceeds that from the diffuse gas. We therefore calculate each term on
the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.

The local sound speed of all identified molecular complexes is much
smaller than their turbulent velocities\footnote{Velocity dispersions
  calculated from velocity field are comparable to those calculated
  from the pressure field 
    \MM{The turbulent pressure field has not been
    mentioned in section 3, so you'll need to add a sentence there
    mentioning its presence and behavior to mention it here}, 
    \DL{AP: also mention turbulent pressure found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a} here?}
indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially 
at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}. 
On average, the Mach number of the MCCs identified at the highest density threshold is $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$, 
but this depends on the evolutionary stage of \flower.  % see e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
We also compute the Mach number from turbulent and thermal pressure to determine the importance of 
differential rotation in the derived velocity dispersion: 
\begin{equation}
\mathcal{M} \equiv \sqrt{\frac{P_{\rm NT} + P}{ P }}\,,
\end{equation}
where $P_{\rm NT}$ is non-thermal pressure and $P$ is thermal pressure.

The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to 
a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
However, not all evolutionary stages considered have at least one MCC at this highest density threshold, 
we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc) in the following. 
We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)}.
\end{equation}
%
We note that the distributions vary for different evolutionary stages of \flower. 
%
The massive ($M_{\rm cl}>$10$^8$\,\Msun) 
clouds identified at low density cut (see top left panel of \Fig{dist})  
correspond to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. Overall, the mass of all MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. The stellar-to-gas mass ratio ranges between $M_{\star}/M_{\rm cl} \simeq$\,0.1\,--\,100 over all the
MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}).

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower.
The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) as they correspond to a large part of \flower, and thus, 
include a large number of stellar mass already ensembled in \flower. 
\label{fig:stellarRatio16}}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{\figpath/alpha_vir_ss21-ss22.png}
\caption{$\alpha_{\rm vir}$-mass relation for pre-starburst (left) and starburst phase. 
Definition of the symbol shown are the same as in \Fig{larsons_single}.
Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$ of MCCs in \flower. 
\label{fig:alpha21-22}}
\end{figure*}

@@

\subsection{Single Evolutionary Stage}  \label{sec:singless}

We present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}), 
and identify a set of MCCs in each of them. 
Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.

Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) 
and sizes ($R\simeq 100$\,pc). These values are consistent with those found in starburst galaxies, 
such as the nearby gas-rich galaxy M64 and 
% Kennicutt, 1996IAUS..171...11K
% Spiral gal, appears to have accreted a gas-rich companion in the recent past, 
% with the inner gas disk the remnant of the
% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995). 
the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs \citep{Heyer04a, Bolatto08a}.

% middle
While the virial parameter is typically defined as Equation~\ref{eqn:alpha} in observational studies, as they probes structures that are 
mainly composed of molecular gas only, we also calculate the total virial parameter ($\alpha_{\rm vir, tot}$; Equation~\ref{eqn:alpha_tot}) 
for MCCs of \flower, given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}). 
MCCs with the highest stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
\Fig{MCC} and \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. 
This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.

% PVE
Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panel of \Fig{larsons_single}.
In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
Dashed lines in the figure show the loci along which the corresponding external pressures are needed for MCCs in equilibrium to have certain 
linewidths for a given set of surface densities (see \Sec{PVE}).
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).

% cloud structures at large and small scale
% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
% column density) as fundamental properties of molecular cloud structure.
Larson's third relation relates MCC structures on small and large
scales via two physical properties: mass and size \citep{Larson81a,
  McKee07a}. This is also known as the constant column density
relation,
\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
  $\Sigma$.  Effectively, Larson's mass-size relation is a single
  point on that relationship, at the constant $\Sigma$ value.  This
  suggests that the mass-size relation is just an artifact of the
  narrow range of column densities observed with $^{12}CO$, as
  suggested among others by \citet{Ballesteros11}.}
since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$). 
% Motivated by \obs, we overplot lines of constants $A_V$ in the mass-size relation shown in \Fig{MR}.
By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
\begin{equation}
A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
\end{equation}
Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
\begin{equation}\label{eqn:constantcolumndensity}
M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
\end{equation}
where we adopt $\mu = 2.5$ as the mean molecular weight.

We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the 
Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
MCCs of \flower spans a 
 lie along the locus of $A_V \simeq 8.9$ clouds observed by
\citet{Lombardi10a} in the MW. 
\MM{Does the variation in surface
  density seen in Figure 7 correspond to the variation in $A_V$ seen
  here?}
%
%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

@@

% Starburst 
In the starburst phase, MCCs have velocity dispersion, sizes,
and virial parameter comparable to those in the accreting phase; however, the MCCs in the starburst phase span 
a wider range in $\sigma^2/R$ and gas surface density. 
Due to a time delay between cloud collapse and \SF, we also examine the virial parameter of MCCs in the pre-starburst phase. 
As shown in \Fig{alpha21-22}, the total virial parameter (blue dots in the figure) 
of a subset of MCCs in the pre-starburst phase are lower than those in the starburst phase of the same mass range. which is as expected.
% None of these MCCs are in the unstable regime ($alpha_{\rm vir} < 2$) because the MCCs are not directly the collapsing structures, 
% i.e., we haven’t reached those scales where true collapse is happening. 
% This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.

\subsection{Temporal Evolution and Adopted Density Threshold Dependence}\label{sec:ncut}

We investigate possible variations in the dynamics of the molecular structures of \flower to test the robustness of our results against the 
choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs. That is, how sensitive are the structure properties, and thus, 
the results presented in \Sec{singless} dependent on the choice of density thresholds.
The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, 
and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$. 
For instance, the cluster of points found at the lowest density threshold, 
occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, 
are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.} ). 
These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel. 
In this way, we identify a population of denser molecular structures (see \Fig{MCC}). 
On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
%% 
%We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
%%
%In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
%%
This lack of variation is reassuring, i.e., our inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in 
nearby and \z$\sim$2 galaxies in the context of linewidth-size relations are not artifacts or biased by our choice of $n_{\rm cut}$ in this work.

%Comparing the left and right panels, the mass range of MCCs identified at the highest density threshold 
%is narrower by about an order of magnitude compared to those identified at the lowest density threshold.
%MCCs identified in the lowest $n_{\rm cut} also have a wider gas surface density. These are a direct manifestation of the decrease in MCC size  
%at increasing $n_{\rm cut}$.

@@

\DL{
1) Note becasuse some MCCs have high stellar-to-gas mass ratios, we plot both gas-only virial parameter 
and the total virial parameter (eqn xx) on the alphavir-mass plots in \Fig{}. The former is used in \obs since 
the quantities are measured using gas tracers. On the other hand, because our MCs are identified with gas density and 
some have high stellar-to-gas mass ratio, influence from the stellar component plays a non-negligible role, as seen in Toomre Q analysis.
% 
2) TODO: Add a plot showing the different alphavir over time. Add a line somewhere that feedback plays in important role in the virial parameter, as 
can be seen in the strong variation in alphavir across the different evolutionary stages of \flower. 
% 
3) add alphavir versus stellar-to-gas mass ratio, 
which shows in the pre-SB phase, we see overall lower alphavir. 
We interpret the alphavir versus stellar-to-gas mass ratio plot as 
1) the general trend is consistent with physics -- alphavir of MCCs are lower compared to other snapshots in the pre-SB phase.  
The reason that we don’t see any MCCs with alphavir $<$ 2 can be understood by realizing that the MCCs are not 
directly the collapsing structures, i.e., we haven’t reached those scales where true collapse is happening.
This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
}
